A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-01-18 doc/large_strain.tex
python: update post-processing script to fit breakdown results with log2

{\color{red}
Figure \ref{fig:roofline} shows results of the Roofline performance model.
As expected, the matrix-based approach is memory bound and (on average) achieves the performance of $8.5\,\rm{GFlop/s}$ (4.5\% of the peak performance) in 2D.
The matrix-free implementations of the fine-strain elastic tangent operator (on average) lead to a much better performance of
$22.1\,\rm{GFlop/s}$ in 2D, as well as about an order of magnitude higher computational intensity, but still stays in the memory-bound regime.
The achieved performance is about 13\% of the peak arithmetic performance. This is much lower than the
70\% reported for the Laplace operator on Cartesian meshes in \cite{kronbichler12}.
Unfortunately, performance measurements for non-Cartesian meshes were not reported in \cite{kronbichler12}.

>>>>

{\color{red}
Figure \ref{fig:roofline} shows results of the Roofline performance model.
As expected, the matrix-based approach is memory bound and (on average) achieves the performance of $8.4\,\rm{GFlop/s}$ (4.5\% of the peak performance) in 2D.
The matrix-free implementations of the fine-strain elastic tangent operator (on average) lead to a much better performance of
$22.0\,\rm{GFlop/s}$ in 2D, as well as about an order of magnitude higher computational intensity, but still stays in the memory-bound regime.
The achieved performance is about 13\% of the peak arithmetic performance. This is much lower than the
70\% reported for the Laplace operator on Cartesian meshes in \cite{kronbichler12}.
Unfortunately, performance measurements for non-Cartesian meshes were not reported in \cite{kronbichler12}.
